Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-05-21 content.tex
Review

  \textbf{1. }
    Phylogenetic trees are current routinely reconstructed from an alignment of character sequences (usually nucleotide sequences). Bayesian tools, such as MrBayes, RevBayes and BEAST2, have gained much popularity over the last decade, as they allow joint estimation of the posterior distribution of the phylogenetic tree and the parameters of the underlying inference model.  
    An important ingredient of these Bayesian approaches is the species tree prior. While in principle the Bayesian framework allows for comparing different species tree priors and hence may elucidate the macroevolutionary processes underlying the species tree, in practice only 
    macroevolutionary models that allow for fast computation of the prior probability are used. 
    This begs the question how accurate the tree estimation is
    when the real macroevolutionary processes are substantially different 
    from those assumed in the tree prior. \\
  \textbf{2. }
    Here we present \verb;pirouette;, 
    a free, libre and open-source R package that assesses 
    the inference error made by Bayesian phylogenetics for a given macroevolutionary diversification model. \verb;pirouette; makes use of BEAST2, but its philosophy applies to any Bayesian phylogenetic inference tool\\
  \textbf{3. }
    We describe \verb;pirouette;'s usage and the biological scientific
    question it can answer, including full examples. \\
  \textbf{4. }
    Last, we discuss the results obtained by the examples and their interpretation. \\
\end{abstract}

@@

\begin{sidewaystable}
\centering
  \begin{tabular}{|p{3.4cm}|p{9.7cm}|p{4.5cm}@{}|}
    \hline
    \centering
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{Sub-argument} & 
    \textbf{Description} &
    \textbf{Possible values} \\ 
    \hline
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;tree_prior; &
    Macroevolutionary diversification model &
    Yule, BD, CBS, CCP, CEP \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;clock_model; &
    Clock for the DNA mutation rates &
    strict, relaxed log-normal \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;site_model; &
    Nucleotide substitution model &
    JC, HKY, TN93, GTR \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;mutation_rate; &
    Pace at which mutation occurs &
    mutation rate $\in \mathbb{R}_{>0}$\\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;root_sequence; &
    DNA sequence at the root of the tree &
    any combination of a, c, g, t \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;model_type; &
    Criterion to select an inference model &
    Generative, Candidate \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;run_if; &
    Condition under which an inference model is used &
    Always, Best candidate \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;do_measure_evidence; &
    Sets whether or not the evidence of the model is to be computed &
    TRUE, FALSE \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;error_function; &
    Specifies how to measure the error &
    nLTT, $|\gamma|$ \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;burn_in_fraction; &
    Specifies the percentage of initial posterior trees to discard &
    \verb;burn_in_fraction; $\in [0, 1]$\\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \hline
  \end{tabular}
  \caption{
    Most important parameter options.
    Yule = pure birth model (\cite{yule})
    BD = birth death (\cite{nee1994reconstructed}), 
    CBS = coalescent Bayesian skyline (\cite{drummond2005bayesian}), 
    CCP = coalescent constant-population, 
    CEP = coalescent exponential-population,
    JC = Jukes and Cantor (\cite{jukes1969evolution}), 
    HKY = Hasegawa, Kishino and Yano (\cite{hasegawa1985dating}), 
    TN93 = Tamura and Nei (\cite{tamura1993estimation}), 
    GTR = Generalized time-reversible model (\cite{tavare1986some}).
  }
  \label{tab:options}
\bigskip

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
  \centering
  \begin{tabular}{ | l | l | l | }
    \hline
    \textbf{Name} & \textbf{Description} & \textbf{Listing} \\
    \hline
    \verb;pir_run; & Run \verb;pirouette; & \ref{lst:pir_run} \\
    \verb;pir_plot; & Show the \verb;pirouette; results as a plot & \ref{lst:pir_plot} \\
    \verb;create_pir_params; & Create the \verb;pirouette; parameters & \ref{lst:create_pir_params} \\
    \hline
    \verb;create_alignment_params; & Create the alignment parameters & \ref{lst:create_alignment_params} \\
    \verb;create_twinning_params; & Create the twinning parameters & \ref{lst:create_twinning_params} \\
    \verb;create_experiment; & Create one experiment & \ref{lst:create_gen_experiment_explicit} \\
    \verb;create_error_measure_params; & Create the error measurement parameters & \ref{lst:create_error_measure_params} \\
    \hline
  \end{tabular}
  \caption{
    \texttt{pirouette}'s main functions, description and the number of the 
    listing in which it is used. 
  }
  \label{tab:functions}
\end{table}
\giovanni{Probably (not 100\% sure) we should make all tables fit within the page limits.}
\richel{Nope, the publisher will do this for us in the end}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

  \textbf{1. }
    Phylogenetic trees are current routinely reconstructed from an alignment 
    of character sequences (usually nucleotide sequences). 
    Bayesian tools, such as MrBayes, RevBayes and BEAST2, 
    have gained much popularity over the last decade, 
    as they allow joint estimation of the posterior distribution of the 
    phylogenetic tree and the parameters of the underlying inference model.  
    An important ingredient of these Bayesian approaches is the species tree 
    prior. While in principle the Bayesian framework allows for comparing 
    different species tree priors and hence may elucidate the macroevolutionary 
    processes underlying the species tree, in practice only 
    macroevolutionary models that allow for fast computation of the prior 
    probability are used. 
    An open question is, how accurate the tree estimation is
    when the real macroevolutionary processes are substantially different 
    from those assumed in the tree prior. \\
  \textbf{2. }
    Here we present \verb;pirouette;, 
    a free, libre and open-source R package that assesses 
    the inference error made by Bayesian phylogenetics for a given 
    macroevolutionary diversification model. \verb;pirouette; makes use of 
    BEAST2, but its philosophy applies to any Bayesian phylogenetic inference 
    tool. \\
  \textbf{3. }
    We describe \verb;pirouette;'s usage and the biological scientific
    question it can answer, including full examples. \\
  \textbf{4. }
    Last, we discuss the results obtained by the examples and their interpretation. \\
\end{abstract}

@@

\begin{sidewaystable}
\centering
  \begin{tabular}{|p{3.4cm}|p{9.7cm}|p{4.5cm}@{}|}
    \hline
    \centering
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{Sub-argument} & 
    \textbf{Description} &
    \textbf{Possible values} \\ 
    \hline
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;tree_prior; &
    Macroevolutionary diversification model &
    Yule, BD, CBS, CCP, CEP \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;clock_model; &
    Clock for the DNA mutation rates &
    strict, relaxed log-normal \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;site_model; &
    Nucleotide substitution model &
    JC, HKY, TN93, GTR \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;mutation_rate; &
    Pace at which mutation occurs &
    \verb;mutation_rate; $\in \mathbb{R}_{>0}$\\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;root_sequence; &
    DNA sequence at the root of the tree &
    any combination of a, c, g, t \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;model_type; &
    Criterion to select an inference model &
    Generative, Candidate \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;run_if; &
    Condition under which an inference model is used &
    Always, Best candidate \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;do_measure_evidence; &
    Sets whether or not the evidence of the model is to be computed &
    TRUE, FALSE \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;error_function; &
    Specifies how to measure the error &
    nLTT, $|\gamma|$ \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;burn_in_fraction; &
    Specifies the percentage of initial posterior trees to discard &
    \verb;burn_in_fraction; $\in [0, 1]$\\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \hline
  \end{tabular}
  \caption{
    Most important parameter options.
    Yule = pure birth model (\cite{yule})
    BD = birth death (\cite{nee1994reconstructed}), 
    CBS = coalescent Bayesian skyline (\cite{drummond2005bayesian}), 
    CCP = coalescent constant-population, 
    CEP = coalescent exponential-population,
    JC = Jukes and Cantor (\cite{jukes1969evolution}), 
    HKY = Hasegawa, Kishino and Yano (\cite{hasegawa1985dating}), 
    TN93 = Tamura and Nei (\cite{tamura1993estimation}), 
    GTR = Generalized time-reversible model (\cite{tavare1986some}).
  }
  \label{tab:options}
\bigskip

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
  \centering
  \begin{tabular}{ | l | l | l | }
    \hline
    \textbf{Name} & \textbf{Description} & \textbf{Listing} \\
    \hline
    \verb;pir_run; & Run \verb;pirouette; & \ref{lst:pir_run} \\
    \verb;pir_plot; & Show the \verb;pirouette; results as a plot & \ref{lst:pir_plot} \\
    \verb;create_pir_params; & Create the \verb;pirouette; parameters & \ref{lst:create_pir_params} \\
    \hline
    \verb;create_alignment_params; & Create the alignment parameters & \ref{lst:create_alignment_params} \\
    \verb;create_twinning_params; & Create the twinning parameters & \ref{lst:create_twinning_params} \\
    \verb;create_experiment; & Create one experiment & \ref{lst:create_gen_experiment_explicit} \\
    \verb;create_error_measure_params; & Create the error measurement parameters & \ref{lst:create_error_measure_params} \\
    \hline
  \end{tabular}
  \caption{
    \texttt{pirouette}'s main functions, description and the number of the 
    listing in which it is used. 
  }
  \label{tab:functions}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-05-21 supplement.tex
Review

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results in detail}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Errors}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Example 1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[ht]
  \centering
  \resizebox {0.8\columnwidth} {!} {
    \begin{tikzpicture}[
      ->,>=stealth',shorten >=1pt,auto,
      node distance=0.25\textheight, 
      semithick
    ]   
    \tikzstyle{every state}=[]
    \node[state, draw=none] (O) [] {
    };   
    \node[state] (A) [right of = O, rectangle] {
      \includegraphics[height=0.2\textheight]{example_1/true_tree.png}
    };   
    \node[state] (B) [below of = A, rectangle] {
      \includegraphics[height=0.2\textheight]{example_1/true_alignment.png}
    };   
    \node[state] (C) [below of = B, rectangle] {
      \includegraphics[height=0.2\textheight]{example_1/true_posterior_gen.png}
    };   
    \node[state] (D) [below of = C, rectangle] {
      \includegraphics[height=0.2\textheight]{example_1/true_error_violin_gen.png}
    };   
    \path 
      (O) edge [anchor = south] node {} (A)
      (A) edge [anchor = south] node {} (B)
      (B) edge [anchor = south] node {} (C)
      (C) edge [anchor = south] node {} (D)
    ; 
    \end{tikzpicture}
  }
  \label{fig:example_1_full_pipeline}
  \caption{Example 1: full pipeline}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Example 5}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[ht]
  \centering
  \resizebox {0.8\columnwidth} {!} {
    \begin{tikzpicture}[
      ->,>=stealth',shorten >=1pt,auto,
      node distance=0.4\textheight, 
      semithick
    ]   
    \tikzstyle{every state}=[]
    \node[state, draw=none] (O) [] {
    };   
    \node[state] (A) [right of = O, rectangle] {
      \includegraphics[height=0.2\textheight]{example_3/true_tree.png}
    };   
    \node[state] (B) [below of = A, rectangle] {
      \includegraphics[height=0.13\textheight]{example_3/true_alignment.png}
    };   
    \node[state] (CG) [below of = B, rectangle] {
      \includegraphics[height=0.2\textheight]{example_3/true_posterior_gen.png}
    };   
    \node[state] (DG) [below of = CG, rectangle] {
      \includegraphics[height=0.2\textheight]{example_3/true_error_violin_gen.png}
    };   
    \node[state] (CB) [right of = C, rectangle] {
      \includegraphics[height=0.2\textheight]{example_3/true_posterior_best.png}
    };   
    \node[state] (DB) [below of = CB, rectangle] {
      \includegraphics[height=0.2\textheight]{example_3/true_error_violin_best.png}
    };   
    \node[state] (AT) [right of = A, rectangle, node distance=0.8\textheight] {
      \includegraphics[height=0.2\textheight]{example_3/twin_tree.png}
    };   
    \node[state] (BT) [below of = AT, rectangle] {
      \includegraphics[height=0.13\textheight]{example_3/twin_alignment.png}
    };   
    \node[state] (CTG) [below of = BT, rectangle] {
      \includegraphics[height=0.2\textheight]{example_3/twin_posterior_gen.png}
    };   
    \node[state] (DTG) [below of = CTG, rectangle] {

\includegraphics[height=0.2\textheight]{example_3/twin_error_violin_gen.png}
    };   
    \node[state] (CTB) [right of = CTG, rectangle] {
      \includegraphics[height=0.2\textheight]{example_3/twin_posterior_best.png}
    };   
    \node[state] (DTB) [below of = CTB, rectangle] {

\includegraphics[height=0.2\textheight]{example_3/twin_error_violin_best.png}
    };   
    \path 
      (O) edge [anchor = south] node {} (A)
      (A) edge [anchor = south] node {} (B)
      (B) edge [anchor = south] node {} (CG)
      (CG) edge [anchor = south] node {} (DG)
      (B) edge [anchor = south east] node {} (CB)
      (CB) edge [anchor = south] node {} (DB)
      (A) edge [anchor = east] node {} (AT)
      (AT) edge [anchor = south] node {} (BT)
      (BT) edge [anchor = south east] node {} (CTG)
      (CTG) edge [anchor = south] node {} (DTG)
      (BT) edge [anchor = south] node {} (CTB)
      (CTB) edge [anchor = south] node {} (DTB)
    ; 
    \end{tikzpicture}
  }
  \label{fig:example_3_full_pipeline}
  \caption{Example 5: full pipeline}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Example 6}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[ht]
  \centering
  \resizebox {0.8\columnwidth} {!} {
    \begin{tikzpicture}[
      ->,>=stealth',shorten >=1pt,auto,
      node distance=0.4\textheight, 
      semithick
    ]   
    \tikzstyle{every state}=[]
    \node[state, draw=none] (O) [] {
    };   
    \node[state] (A) [right of = O, rectangle] {
      \includegraphics[height=0.2\textheight]{example_2/true_tree.png}
    };   
    \node[state] (B) [below of = A, rectangle] {
      \includegraphics[height=0.13\textheight]{example_2/true_alignment.png}
    };   
    \node[state] (CG) [below of = B, rectangle] {
      \includegraphics[height=0.2\textheight]{example_2/true_posterior_gen.png}
    };   
    \node[state] (DG) [below of = CG, rectangle] {
      \includegraphics[height=0.2\textheight]{example_2/true_error_violin_gen.png}
    };   
    \node[state] (CB) [right of = C, rectangle] {
      \includegraphics[height=0.2\textheight]{example_2/true_posterior_best.png}
    };   
    \node[state] (DB) [below of = CB, rectangle] {
      \includegraphics[height=0.2\textheight]{example_2/true_error_violin_best.png}
    };   
    \path 
      (O) edge [anchor = south] node {} (A)
      (A) edge [anchor = south] node {} (B)
      (B) edge [anchor = south] node {} (CG)
      (CG) edge [anchor = south] node {} (DG)
      (B) edge [anchor = south east] node {} (CB)
      (CB) edge [anchor = south] node {} (DB)
    ; 
    \end{tikzpicture}
  }
  \label{fig:example_2_full_pipeline}
  \caption{Example 6: full pipeline}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Supplementary materials}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Usage with generative model}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
  \centering
  \resizebox {0.8\columnwidth} {!} {
    \begin{tikzpicture}[
      ->,>=stealth',shorten >=1pt,auto,
      node distance=0.25\textheight, 
      semithick
    ]   
    \tikzstyle{every state}=[]
    \node[state, draw=none] (O) [] {
    };   
    \node[state] (A) [right of = O, rectangle] {
      \includegraphics[height=0.2\textheight]{example_1/true_tree.png}
    };   
    \node[state] (B) [below of = A, rectangle] {
      \includegraphics[height=0.2\textheight]{example_1/true_alignment.png}
    };   
    \node[state] (C) [below of = B, rectangle] {
      \includegraphics[height=0.2\textheight]{example_1/true_posterior_gen.png}
    };   
    \node[state] (D) [below of = C, rectangle] {
      \includegraphics[height=0.2\textheight]{example_1/true_error_violin_gen.png}
    };   
    \path 
      (O) edge [anchor = south] node {} (A)
      (A) edge [anchor = south] node {} (B)
      (B) edge [anchor = south] node {} (C)
      (C) edge [anchor = south] node {} (D)
    ; 
    \end{tikzpicture}
  }
  \label{fig:example_1_full_pipeline}
  \caption{Example 1: full pipeline}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Usage with generative and candidate models}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
  \centering
  \resizebox {0.8\columnwidth} {!} {
    \begin{tikzpicture}[
      ->,>=stealth',shorten >=1pt,auto,
      node distance=0.7\textheight, 
      semithick
    ]   
    \tikzstyle{every state}=[]
    \node[state, draw=none] (O) [] {
    };   
    \node[state] (A) [right of = O, rectangle] {
      \includegraphics[height=0.5\textheight]{example_2/true_tree.png}
    };   
    \node[state] (B) [below of = A, rectangle] {
      \includegraphics[height=0.5\textheight]{example_2/true_alignment.png}
    };   
    \node[state] (CG) [below of = B, rectangle] {
      \includegraphics[height=0.45\textheight]{example_2/true_posterior_gen.png}
    };   
    \node[state] (DG) [below of = CG, rectangle] {
      \includegraphics[height=0.3\textheight]{example_2/true_error_violin_gen.png}
    };   
    \node[state] (CB) [right of = CG, rectangle] {
      \includegraphics[height=0.45\textheight]{example_2/true_posterior_best.png}
    };   
    \node[state] (DB) [right of = DG, rectangle] {
      \includegraphics[height=0.3\textheight]{example_2/true_error_violin_best.png}
    };   
    \path 
      (O) edge [anchor = south] node {} (A)
      (A) edge [anchor = south] node {} (B)
      (B) edge [anchor = south] node {} (CG)
      (CG) edge [anchor = south] node {} (DG)
      (B) edge [anchor = south] node {} (CB)
      (CB) edge [anchor = south] node {} (DB)
    ; 
    \end{tikzpicture}
  }
  \label{fig:example_2_full_pipeline}
  \caption{Usage with generative and candidate models: full pipeline}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Usage with generative and candidate models, compared to the background noise}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
  \centering
  \resizebox {1.0\columnwidth} {!} {
    \begin{tikzpicture}[
      ->,>=stealth',shorten >=1pt,auto,
      node distance=0.5\textheight, 
      semithick
    ]   
    \tikzstyle{every state}=[]
    \node[state, draw=none] (O) [] {
    };   
    \node[state] (A) [right of = O, rectangle] {
      \includegraphics[height=0.4\textheight]{example_3/true_tree.png}
    };   
    \node[state] (B) [below of = A, rectangle] {
      \includegraphics[height=0.25\textheight]{example_3/true_alignment.png}
    };   
    \node[state] (CG) [below of = B, rectangle] {
      \includegraphics[height=0.3\textheight]{example_3/true_posterior_gen.png}
    };   
    \node[state] (DG) [below of = CG, rectangle] {
      \includegraphics[height=0.3\textheight]{example_3/true_error_violin_gen.png}
    };   
    \node[state] (CB) [right of = CG, rectangle] {
      \includegraphics[height=0.3\textheight]{example_3/true_posterior_best.png}
    };   
    \node[state] (DB) [below of = CB, rectangle] {
      \includegraphics[height=0.3\textheight]{example_3/true_error_violin_best.png}
    };   
    \node[state] (AT) [right of = A, rectangle, node distance=0.8\textheight] {
      \includegraphics[height=0.4\textheight]{example_3/twin_tree.png}
    };   
    \node[state] (BT) [below of = AT, rectangle] {
      \includegraphics[height=0.25\textheight]{example_3/twin_alignment.png}
    };   
    \node[state] (CTG) [right of = CB, rectangle] {
      \includegraphics[height=0.3\textheight]{example_3/twin_posterior_gen.png}
    };   
    \node[state] (DTG) [below of = CTG, rectangle] {
      \includegraphics[height=0.3\textheight]{example_3/twin_error_violin_gen.png}
    };   
    \node[state] (CTB) [right of = CTG, rectangle] {
      \includegraphics[height=0.3\textheight]{example_3/twin_posterior_best.png}
    };   
    \node[state] (DTB) [below of = CTB, rectangle] {
      \includegraphics[height=0.3\textheight]{example_3/twin_error_violin_best.png}
    };   
    \path 
      (O) edge [anchor = south] node {} (A)
      (A) edge [anchor = south] node {} (B)
      (B) edge [anchor = south] node {} (CG)
      (CG) edge [anchor = south] node {} (DG)
      (B) edge [anchor = south east] node {} (CB)
      (CB) edge [anchor = south] node {} (DB)
      (A) edge [anchor = east] node {} (AT)
      (AT) edge [anchor = south] node {} (BT)
      (BT) edge [anchor = south east] node {} (CTG)
      (CTG) edge [anchor = south] node {} (DTG)
      (BT) edge [anchor = south] node {} (CTB)
      (CTB) edge [anchor = south] node {} (DTB)
    ; 
    \end{tikzpicture}
  }
  \label{fig:example_3_full_pipeline}
  \caption{Usage with generative and candidate models, compared to the background noise: full pipeline}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Runtime}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@
